\title{Flashless}
\acknowledge{Portions Copyright \tm{ClickToFlash Developers} 2009.}

\newcommand{\about}{%
\begin{intro}[useless.github.com/flashless]
A WebKit plug-in to display preview images for Flash based video services and block the rest.
\end{intro}}

\newcommand{\install}{%
\section{Installation}
\emph{\tm{Mac OS X 10.5 } ``Leopard" or later required.}

Quit \tm{Safari}.
Drag the icon labeled \emph{Flashless.webplugin} from the disk image to the icon labeled \emph{Internet Plug-Ins}.
You can now relaunch \tm{Safari}. Done.

\begin{note}
This will install \tm{Flashless} for all users.
To install just for the current user, copy \emph{Flashless.webplugin} to \code{\textasciitilde/Library/Internet Plug-Ins} instead.
\end{note}
}

\newcommand{\usage}{%
\section{Usage}

Flashless replaces all Flash elements on a site with an unobtrusive graphic.
To show the original Flash object just click on the placeholder.

A preview image of the video is displayed for content from a supported video service.
The name of the service is displayed in the lower right corner.

You can use these modifier keys:
\begin{multicols}{2}
\emph{Command} \dotfill\ jump to original video site \\
\emph{Option} \dotfill\ download the video \\
\emph{Shift} \dotfill\ play with Flash \\
\emph{Control} \dotfill\ show the menu
\end{multicols}

Not all features are available for all sites.
}

\newcommand{\copylicense}{%
\begin{license}[2009--\the\year]
Permission is hereby granted, free of charge, to any person
obtaining a copy of this software and associated documentation
files (the ``Software"), to deal in the Software without restriction,
including without limitation the rights to use, copy, modify, merge,
publish, distribute, sublicense, and/or sell copies of the Software,
and to permit persons to whom the Software is furnished to do so,
subject to the following conditions:

The above copyright notice and this permission notice shall be
included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED ``AS IS", WITHOUT WARRANTY OF ANY KIND,
EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES
OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT
HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY,
WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
OTHER DEALINGS IN THE SOFTWARE.
\end{license}}
